---
title: "river-quality-data-processing"
author: "Vikas Maturi"
output: 
  github_document:
    toc: true
    toc_depth: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries and Parameters
```{r}
library(tidyverse)
#library(rvest)
library(lubridate)
```

```{r}
#url_data <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv?cb_00010=on&cb_00065=on&cb_00480=on&format=html&site_no=301429089145600&period=&begin_date=2018-11-30&end_date=2019-10-03"

#url_data_test_tsv <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv/?cb_00010=on&cb_00065=on&cb_00300=on&cb_00480=on&cb_63680=on&format=rdb&site_no=301912088583300&period=&begin_date=2018-10-01&end_date=2019-10-01"

#url_data_4years <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv/?cb_00010=on&cb_00065=on&cb_00300=on&cb_00480=on&cb_63680=on&format=rdb&site_no=301912088583300&period=&begin_date=2015-10-01&end_date=2019-10-01"

url_east_ship <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv/?cb_00010=on&cb_00065=on&cb_00300=on&cb_00480=on&cb_63680=on&format=rdb&site_no=301527088521500&period=&begin_date=2015-10-01&end_date=2019-10-01"

url_east_ship_7 <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv/?cb_00010=on&cb_00065=on&cb_00300=on&cb_00480=on&cb_63680=on&format=rdb&site_no=301527088521500&period=&begin_date=2012-10-01&end_date=2019-10-01"

url_biloxi_7 <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv?cb_00010=on&cb_00065=on&cb_00480=on&format=rdb&site_no=302318088512600&period=&begin_date=2012-10-01&end_date=2019-10-01"

url_gulfport_7 <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv/?cb_00010=on&cb_00065=on&cb_00300=on&cb_00480=on&cb_63680=on&format=rdb&site_no=301912088583300&period=&begin_date=2012-10-01&end_date=2019-10-01"

url_st_joseph_7 <- "https://nwis.waterdata.usgs.gov/ms/nwis/uv/?cb_00010=on&cb_00065=on&cb_00480=on&format=rdb&site_no=301104089253400&period=&begin_date=2012-10-01&end_date=2019-10-01"
```




# Reading in data from various sites 

## Reading in East Ship Island Site data (4 years)
```{r}
east_ship <- 
  read_tsv(
    url_east_ship, 
    col_names = FALSE,
    col_types =
      cols(
        X1 = col_character(),
        X2 = col_double(),
        X3 = col_datetime(format = ""),
        X4 = col_character(),
        X5 = col_double(),
        X6 = col_character(),
        X7 = col_double(),
        X8 = col_character(),
        X9 = col_double(),
        X10 = col_character(),
        X11 = col_double(),
        X12 = col_character(),
        X13 = col_double(),
        X14 = col_character()
      ),
    comment = "#",
    skip = 50
  ) %>% 
  rename(
    "agency_cd" = X1,
    "site_no" = X2,
    "date_time" = X3,
    "timezone" = X4,
    "gage_height" = X5,
    "gage_app_prov" = X6,
    "temperature" = X7,
    "temp_app_prov" = X8,
    "turbidity" = X9,
    "turb_app_prov" = X10,
    "dissolvedh20" = X11,
    "diss_app_prov" = X12,
    "salinity" = X13,
    "sal_app_prov" = X14,
  ) %>% 
  mutate(temperature = as.double(temperature))
```

## Reading in East Ship Island site data (7 years)
```{r}
east_ship_7 <- 
  read_tsv(
    url_east_ship_7, 
    col_names = FALSE,
    col_types =
      cols(
        X1 = col_character(),
        X2 = col_double(),
        X3 = col_datetime(format = ""),
        X4 = col_character(),
        X5 = col_double(),
        X6 = col_character(),
        X7 = col_double(),
        X8 = col_character(),
        X9 = col_double(),
        X10 = col_character(),
        X11 = col_double(),
        X12 = col_character(),
        X13 = col_double(),
        X14 = col_character()
      ),
    comment = "#",
    skip = 50
  ) %>% 
  rename(
    "agency_cd" = X1,
    "site_no" = X2,
    "date_time" = X3,
    "timezone" = X4,
    "gage_height" = X5,
    "gage_app_prov" = X6,
    "temperature" = X7,
    "temp_app_prov" = X8,
    "turbidity" = X9,
    "turb_app_prov" = X10,
    "dissolvedh20" = X11,
    "diss_app_prov" = X12,
    "salinity" = X13,
    "sal_app_prov" = X14,
  ) %>% 
  mutate(temperature = as.double(temperature))
```



## Reading in Biloxi site data (7 years)
```{r}
biloxi_7 <- 
  read_tsv(
    url_biloxi_7, 
    col_names = FALSE,
    col_types =
      cols(
        X1 = col_character(),
        X2 = col_double(),
        X3 = col_datetime(format = ""),
        X4 = col_character(),
        X5 = col_double(),
        X6 = col_character(),
        X7 = col_double(),
        X8 = col_character(),
        X9 = col_double(),
        X10 = col_character()
      ),
    comment = "#",
    skip = 50
  ) %>% 
  rename(
    "agency_cd" = X1,
    "site_no" = X2,
    "date_time" = X3,
    "timezone" = X4,
    "temperature" = X5,
    "temp_app_prov" = X6,
    "gage_height" = X7,
    "gage_app_prov" = X8,
    "salinity" = X9,
    "sal_app_prov" = X10,
  ) %>% 
  mutate(temperature = as.double(temperature))
```

## Reading in St. Joseph (7 years)
```{r}
stjoseph <- 
  read_tsv(
    url_st_joseph_7, 
    col_names = FALSE,
    col_types =
      cols(
        X1 = col_character(),
        X2 = col_double(),
        X3 = col_datetime(format = ""),
        X4 = col_character(),
        X5 = col_double(),
        X6 = col_character(),
        X7 = col_double(),
        X8 = col_character(),
        X9 = col_double(),
        X10 = col_character()
      ),
    comment = "#",
    skip = 50
  ) %>% 
  rename(
    "agency_cd" = X1,
    "site_no" = X2,
    "date_time" = X3,
    "timezone" = X4,
    "gage_height" = X5,
    "gage_app_prov" = X6,
    "temperature" = X7,
    "temp_app_prov" = X8,
    "salinity" = X9,
    "sal_app_prov" = X10,
  ) %>% 
  mutate(temperature = as.double(temperature))
```


## Reading in Gufport site data (7 years)
```{r}
gulfport <- 
  read_tsv(
    url_gulfport_7, 
    col_names = FALSE,
    col_types =
      cols(
        X1 = col_character(),
        X2 = col_double(),
        X3 = col_datetime(format = ""),
        X4 = col_character(),
        X5 = col_double(),
        X6 = col_character(),
        X7 = col_double(),
        X8 = col_character(),
        X9 = col_double(),
        X10 = col_character(),
        X11 = col_double(),
        X12 = col_character(),
        X13 = col_double(),
        X14 = col_character()
      ),
    comment = "#",
    skip = 50
  ) %>% 
  rename(
    "agency_cd" = X1,
    "site_no" = X2,
    "date_time" = X3,
    "timezone" = X4,
    "gage_height" = X5,
    "gage_app_prov" = X6,
    "temperature" = X7,
    "temp_app_prov" = X8,
    "salinity" = X9,
    "sal_app_prov" = X10,
    "turbidity" = X11,
    "turb_app_prov" = X12,
    "dissolvedh20" = X13,
    "diss_app_prov" = X14
  ) %>% 
  mutate(temperature = as.double(temperature))
```

## Reading in TEST data
```{r, include = FALSE, eval = FALSE}
#previous approach to storing column names
# names_usgs_data <- 
#   read_tsv(url_data_tsv, col_names = FALSE, n_max = 1, comment ="#") %>% 

#reading in the test data set (1 year), casting column types and renaming columns.
usgs_data_test <- 
  read_tsv(
    url_data_test_tsv, 
    col_names = FALSE,
    col_types =
      cols(
        agency_cd = col_character(),
        site_no = col_double(),
        date_time = col_datetime(format = ""),
        timezone = col_character(),
        gage_height = col_double(),
        gage_app_prov = col_character(),
        temperature = col_double(),
        temp_app_prov = col_character(),
        salinity = col_double(),
        sal_app_prov = col_character(),
        turbidity = col_double(),
        turb_app_prov = col_character(),
        dissolvedh20 = col_double(),
        diss_app_prov = col_character()
      ),
    comment = "#",
    skip = 50
  ) %>% 
  rename(
    "agency_cd" = X1,
    "site_no" = X2,
    "date_time" = X3,
    "timezone" = X4,
    "gage_height" = X5,
    "gage_app_prov" = X6,
    "temperature" = X7,
    "temp_app_prov" = X8,
    "salinity" = X9,
    "sal_app_prov" = X10,
    "turbidity" = X11,
    "turb_app_prov" = X12,
    "dissolvedh20" = X13,
    "diss_app_prov" = X14
  ) %>% 
  mutate(temperature = as.double(temperature))

# names(usgs_data_test) <- names_usgs_data
```



 



# Exploratory Analysis

## Additional graph filtering
```{r}
#calculating the average daily salinity, temperature, turbidity - east ship island (4 years)
daily_averages_east_ship <-
  east_ship %>% 
  mutate(date = date(date_time)) %>% 
  group_by(date) %>% 
  summarize(
    sal_mean = mean(salinity, na.rm = TRUE),
    temp_mean = mean(temperature, na.rm = TRUE),
    turb_mean = mean(turbidity, na.rm = TRUE),
    H20_mean = mean(dissolvedh20, na.rm = TRUE)
    ) %>% 
  arrange(date)

#calculating the average daily salinity, temperature, turbidity - east ship island (7 years)
daily_averages_east_ship_7 <-
  east_ship_7 %>% 
  mutate(date = date(date_time)) %>% 
  group_by(date) %>% 
  summarize(
    sal_mean = mean(salinity, na.rm = TRUE),
    temp_mean = mean(temperature, na.rm = TRUE),
    turb_mean = mean(turbidity, na.rm = TRUE),
    H20_mean = mean(dissolvedh20, na.rm = TRUE)
    ) %>% 
  arrange(date)


#calculating the average daily salinity, temperature, turbidity - biloxi (7 years)
daily_averages_biloxi_7 <-
  biloxi_7 %>% 
  mutate(date = date(date_time)) %>% 
  group_by(date) %>% 
  summarize(
    sal_mean = mean(salinity, na.rm = TRUE),
    temp_mean = mean(temperature, na.rm = TRUE),
    gage_mean = mean(gage_height, na.rm = TRUE)
    ) %>% 
  arrange(date)


#calculating the average daily salinity, temperature, turbidity - gulfport (7 years)
daily_averages_gulfport <-
  gulfport %>% 
  mutate(date = date(date_time)) %>% 
  group_by(date) %>% 
  summarize(
    sal_mean = mean(salinity, na.rm = TRUE),
    temp_mean = mean(temperature, na.rm = TRUE),
    gage_mean = mean(gage_height, na.rm = TRUE)
    ) %>% 
  arrange(date)

#calculating the average daily salinity, temperature, turbidity - st joseph (7 years)
daily_averages_stjoseph <-
  stjoseph %>% 
  mutate(date = date(date_time)) %>% 
  group_by(date) %>% 
  summarize(
    sal_mean = mean(salinity, na.rm = TRUE),
    temp_mean = mean(temperature, na.rm = TRUE),
    gage_mean = mean(gage_height, na.rm = TRUE)
    ) %>% 
  arrange(date)
  
```


#Daily Average Temperature in East Ship Island (4 years)
```{r}
daily_averages_east_ship %>% 
  ggplot(mapping = aes(x = date, y = temp_mean)) +
  geom_line() +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue")
```


#Daily Average Turbidity in East Ship Island (4 years)
```{r}
daily_averages_east_ship %>% 
  ggplot(mapping = aes(x = date, y = turb_mean)) +
  geom_line() +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue")
```


#Daily Average Salinity in East Ship Island (4 years)
```{r}
daily_averages_east_ship %>% 
  ggplot(mapping = aes(x = date, y = sal_mean)) +
  geom_line() +
  theme_light() +
  theme(
    panel.grid.minor = element_blank()
  ) +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue") +
  #text annotations
  annotate("text", x = date("2019-03-01"), y = 7, label = "Salinity drop \ninconsistent with \nhistorical trends ", hjust = "right", ) +
  labs(
    title = "Average daily salinity over time",
    subtitle = "Bonnet Carre spillway openings in blue",
    x = "Date",
    y = "Average daily salinity"
  ) 
## ADD SCALES TO THIS GRAPH!! b

```

We see a significant drop in salinity levels in 2019, despite consistent levels in years prior (even during spillway openings).


#Daily Average Salinity in Biloxi (7 years)
```{r}
daily_averages_biloxi_7 %>% 
  ggplot(mapping = aes(x = date, y = sal_mean)) +
  geom_line() +
  theme_light() +
  theme(
  ) +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue") +
  #text annotations
  labs(
    title = "Average daily salinity over time",
    subtitle = "Bonnet Carre spillway openings in blue",
    x = "Date",
    y = "Average daily salinity"
  ) 
## ADD SCALES TO THIS GRAPH!! b

```
At the Biloxi site, we see no obvious drop beyond other sites, but we do see a clear change in the frequency of salinity shifts (up and down drops) - they appear more frequent and less regular moving past 2016. 


# Daily Average Salinity in Gulfport (7 years)
```{r}
daily_averages_gulfport %>% 
  ggplot(mapping = aes(x = date, y = sal_mean)) +
  geom_line() +
  theme_light() +
  theme(
  ) +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue") +
  #text annotations
  labs(
    title = "Average daily salinity over time",
    subtitle = "Bonnet Carre spillway openings in blue",
    x = "Date",
    y = "Average daily salinity"
  ) 
## ADD SCALES TO THIS GRAPH!! b
```

# Daily Average Salinity in St. Joseph (7 years)
```{r}
daily_averages_stjoseph %>% 
  ggplot(mapping = aes(x = date, y = sal_mean)) +
  geom_line() +
  theme_light() +
  theme(
  ) +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue") +
  #text annotations
  labs(
    title = "Average daily salinity over time",
    subtitle = "Bonnet Carre spillway openings in blue",
    x = "Date",
    y = "Average daily salinity"
  ) 
## ADD SCALES TO THIS GRAPH!! b
```


#Daily Average Salinity in East Ship Island (7 years)
```{r}
daily_averages_east_ship_7 %>% 
  ggplot(mapping = aes(x = date, y = sal_mean)) +
  geom_line() +
  #Markers of the fur main spillway openings
  geom_vline(aes(xintercept = date("2016-01-10")), color = "blue") + 
  geom_vline(aes(xintercept = date("2018-03-08")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-02-27")), color = "blue") + 
  geom_vline(aes(xintercept = date("2019-05-10")), color = "blue") 
```

Looking at more historical trends, we notice no salinity drop has been as significant as the 2019 drop after 2 spillway openings. 
 