---
title: "taxi-raining-analysis"
output: 
  github_document:
    toc: trues
    toc_depth: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries and Parameters
```{r}
#load libraries
library(tidyverse)
library(lubridate)
library(scales)
```

```{r}
#save local file names
precip_data <- "~/MSE231/HW2/nyc_precipitation.csv"

test_taxi <- "~/MSE231/HW2/drivers_onduty.tsv"

file_taxi_1 <- "~/MSE231/HW2/part-00000"
file_taxi_2 <- "~/MSE231/HW2/part-00001"
file_taxi_3 <- "~/MSE231/HW2/part-00002"
file_taxi_4 <- "~/MSE231/HW2/part-00003"
file_taxi_5 <- "~/MSE231/HW2/part-00004"


```


# Read in Data
```{r}
#read in precipitation data
precipitation <- 
  read_csv(
    precip_data
  )

taxi_test <- 
  read_tsv(
    test_taxi,
    col_names = c("date", "hour", "drivers_onduty", "t_onduty", "t_occupied", "n_pass", "n_trip", "n_mile", "earnings")
  ) %>% 
  mutate(
    datetime = as_datetime(paste(date, hour))
  )

taxi <-
  read_tsv(file_taxi_1, col_names = c("date", "hour", "drivers_onduty", "t_onduty", "t_occupied", "n_pass", "n_trip", "n_mile", "earnings")) %>% 
  bind_rows(read_tsv(file_taxi_2, col_names = c("date", "hour", "drivers_onduty", "t_onduty", "t_occupied", "n_pass", "n_trip", "n_mile", "earnings"))) %>% 
  bind_rows(read_tsv(file_taxi_3, col_names = c("date", "hour", "drivers_onduty", "t_onduty", "t_occupied", "n_pass", "n_trip", "n_mile", "earnings"))) %>% 
  bind_rows(read_tsv(file_taxi_4, col_names = c("date", "hour", "drivers_onduty", "t_onduty", "t_occupied", "n_pass", "n_trip", "n_mile", "earnings"))) %>%  
  bind_rows(read_tsv(file_taxi_5, col_names = c("date", "hour", "drivers_onduty", "t_onduty", "t_occupied", "n_pass", "n_trip", "n_mile", "earnings"))) %>% 
  mutate(
    datetime = as_datetime(paste(date, hour))
  )
```

```{r}
precipitation %>% 
  filter(
    date(DATE) == date("2013-01-14")
  )
```


# Part 6: Left-join precipitation data with taxi data
```{r}
taxi_rain <-
  left_join(
    taxi, 
    precipitation %>% select("DATE", "HPCP"), 
    by = c("datetime" = "DATE")
  ) %>% 
  select(date, hour, precip = "HPCP", everything()) %>% 
  # if there is no value listed in the precipitation gauge, we assume 0 (we need to confirm this assumtion)
  mutate(
    precip = if_else(is.na(precip), 0, precip),
    raining = if_else(precip == 0, 'No Rain', "Rain")
  )

```


# Part 7 [Step 1]: Average hourly wage of taxi drivers through day in different rain conditions
As a first step, plot the average hourly wage of taxi drivers throughout the day, both when it rains and when it doesn't. Specifically, create a single plot where the x-axis corresponds to the 24 hours of the day, the y-axis is average hourly wage, and there are separate lines for periods during which it rained and which it did not. ("Rain" is being used as shorthand for "precipitation", which may include both rain and snowfall.)
```{r}
taxi_rain %>% 
  mutate(
    hourly_wage = earnings / t_onduty
  ) %>% 
  group_by(hour, raining) %>% 
  summarize(avg_hourly_wage = mean(hourly_wage, na.rm = TRUE)) %>% 
  ggplot(mapping = aes(x = hour, y = avg_hourly_wage)) +
  geom_line(aes(group = raining, color = raining)) + 
  theme_bw() +
  labs(
    x = "Hour",  
    y = "Average hourly wage",
    title = "Average hourly wage per hour in different rain conditions"
  )


```

# Part 7 Step 2: Average hourly 
Carry out similar analyses for supply and demand. In particular, explore various ways to quantify supply and demand (there are multiple reasonable approaches), with the goal of understanding why it's harder to catch a cab in the rain.
```{r}

taxi_sd <-
  taxi_rain %>% 
  # t_supply may be easily measured as a function of the number of drivers on dut
  # t_demand is well measured by the amount of time that a driver is on-duty but not taking people. There is more supply if there are many drivers spending a lot of time on duty but unoccupied
  mutate(t_demand = t_onduty - t_occupied) %>% 
  mutate(pct_demand = t_occupied / t_onduty) 

```

We assume supply can be measured purely by the number of drivers on duty. 
```{r}
taxi_sd %>% 
  group_by(hour, raining) %>% 
  summarize(
    avg_drivers_onduty = mean(drivers_onduty, na.rm = TRUE)
  ) %>% 
  ggplot(mapping = aes(x = hour, y = avg_drivers_onduty)) +
  geom_line(aes(group = raining, color = raining)) + 
  theme_bw() +
  labs(
    x = "Hour",  
    y = "Average supply (drivers onduty)",
    title = "Average supply (drivers onduty) per hour in different rain conditions"
  )
```
We assume demand can be measured by the percentage of time that drivers are actually carrying passengers (time_occupied / time_onduty)

```{r}
demandperhour <-
  taxi_sd %>%   
  group_by(hour, raining) %>% 
  summarize(
    avg_pct_occupied = mean(pct_demand, na.rm = TRUE)
  ) %>% 
  ggplot(mapping = aes(x = hour, y = avg_pct_occupied)) +
  geom_line(aes(group = raining, color = raining)) + 
  theme_bw() +
  scale_colour_manual('', breaks = c('Rain', 'No Rain'), values = c('red', 'blue')) +
  # scale_y_continuous(breaks = seq(0, 1000 * ceiling(max(pelosi_gender_clean$female, pelosi_gender_clean$male) / 1000), 500)) +
  labs(
    x = "Hour",  
    y = "Average demand",
    title = "Average demand per hour in different rain conditions"
  ) 

demandperhour

## Save plot
ggsave('test_demand_hour.pdf', width = 7, height = 5, plot = demandperhour)

  
```



# Testing stuff
```{r, eval = FALSE}
test_driver_stats <- read_tsv("~/MSE231/HW2/driver_stats.tsv", col_names = FALSE)

test_driver_stats %>% 
  filter(hour(X2) == hour(as_datetime("2018-01-01 23:00:00")))

test_driver_onduty_map <- read_tsv("~/MSE231/HW2/drivers_onduty_map.tsv", col_names = FALSE)
```

